Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-06-04 manuscript/manuscript.Rmd
Progress on manuscript and ML analysis.

>>>>

We used 285 datasets from the Penn Machine Learning Benchmarks collection [@].
In this collection, 122 datasets correspond to regression tasks and 163 datasets to classification tasks.
Using the familiar auto-machine learning library [@], each dataset was used to train a model for each of 16 process configurations.
Each process configuration specifies the learner (generalised linear model or random forest), 
transformation method (none, conventional Yeo-Johnson, robust invariant Yeo-Johnson, robust invariant Yeo-Johnson with empirical central normality test ($p = 0.01$)),
and normalisation method (none, $z$-standardisation), yielding 16 distinct configurations.

Before each experiment, each dataset was randomly split into a training (70%) and holdout test (30%) set five times. Thus, a total of 22800 models were created.
Each model was then evaluated using the holdout test set.

- Plot differences vs. none transformation method.
- Plot differences vs. none normalisation method and conventional transformation.
